Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-14 WSSSPE2_report/WSSSPE2_review.tex
Section Section 4: touch up.

\item \textbf{Robert R. Downs: Community Recommendations for Improving Sustainable
Scientific Software Practices.}
Robert R. Downs, of the Columbia University Center for International Earth
Science Information Network (CIESIN), 
%presented Community Recommendations for
%Improving Sustainable Scientific Software Practices (2014), and 
described a
focus group study that was conducted with W. Christopher Lenhardt, Erin Robinson, Ethan Davis, and Nicholas
Weber of the Science Software
Cluster of the Federation of Earth Science Information Partners (ESIP). For the study, almost 300 attendees of the 2014 Summer ESIP Meeting were
invited to participate in simultaneous roundtable discussions on  
sustainability of science software. Over two-thirds of the roundtable focus
groups   responded to a semi-structured survey that contained
three sets of questions eliciting recommendations for near-term actions of the
community to improve sustainable software practices. Initial analysis of the participants' responses to the questionnaire
 revealed several suggestions, which  included improving community engagement and collaborative
activities, increasing understanding and awareness, and creating incentives to
motivate sustainable science software practices. 
%Based on the recommendations
%offered by the focus group respondents for near-term actions, 
The ESIP Science
Software Cluster plans to engage the community to achieve progress in the near
future on the recommended activities for improving sustainable scientific
software practices.

>>>>

\item \textbf{Robert Downs: Community Recommendations for Improving Sustainable
Scientific Software Practices.}
Robert Downs, of the Columbia University Center for International Earth
Science Information Network (CIESIN), 
%presented Community Recommendations for
%Improving Sustainable Scientific Software Practices (2014), and 
described a
focus group study that was conducted with W. Christopher Lenhardt, Erin Robinson, Ethan Davis, and Nicholas
Weber of the Science Software
Cluster of the Federation of Earth Science Information Partners (ESIP). For the study, almost 300 attendees of the 2014 Summer ESIP Meeting were
invited to participate in simultaneous roundtable discussions on  
sustainability of science software. Over two-thirds of the roundtable focus
groups   responded to a semi-structured survey that contained
three sets of questions eliciting recommendations for near-term actions of the
community to improve sustainable software practices. Initial analysis of the participants' responses to the questionnaire
 revealed several suggestions, which  included improving community engagement and collaborative
activities, increasing understanding and awareness, and creating incentives to
motivate sustainable science software practices. 
%Based on the recommendations
%offered by the focus group respondents for near-term actions, 
The ESIP Science
Software Cluster plans to engage the community to achieve progress in the near
future on the recommended activities for improving sustainable scientific
software practices.
